---
title: "Creating Map from Shapefile "
output: html_notebook
editor_options: 
  chunk_output_type: console
---

## Get all Library Needed to Make this Happen!

```{r setup}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = FALSE
)

library(tidyverse)
library(scales)
library(ggthemes)
library(hrbrthemes)
library(sf) 
library(glue)
library(ggrepel)

```



## Prepping Things by Downloading What's Needed

```{r getIngredientTogether}

# Download Shapefile from ESRI site (For Japan map, I donwloaded from below)
# https://www.esrij.com/products/japan-shp/

japan.map <- sf::read_sf("Shapefiles/japan_ver81/japan_ver81.shp")
japan.map <- japan.map %>% mutate(pref_cd = str_sub(JCODE,1L,2L), pref_no = as.integer(pref_cd))

## Read Other Files 
train.lines.df <- read_rds("Data/JapanStationData.rds")
japan.prefecture <- read_rds("Data/JapanPrefecture.rds")

```


## Because I want all map to look similar, I'm setting up global theme!

```{r global_map_theme}

theme_map_chi <- function(...) {
  theme_minimal() +
  theme(
    text = element_text(family = "Hiragino Sans W3", color = "black"),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(color = "#ebebe5", size = 0.2),
    panel.grid.minor = element_blank(),
    plot.background = element_rect(fill = "#ffffff", color = NA), 
    panel.background = element_rect(fill = "#ffffff", color = NA), 
    legend.background = element_rect(fill = "#ffffff", color = NA),
    panel.border = element_blank(),
    ...
  )
}

```




```{r}
## I want station that has transfers of lines
major.station <- train.lines.df %>% ungroup() %>%
  group_by(prefs_cd ,station) %>%
  summarise(n=n(),lat=mean(lat), lon=mean(lon), 
            line.name.list = paste(line.name, collapse="|")) %>%
  filter(n>1) %>%
  mutate(pref_no = as.integer(prefs_cd)) %>%
  group_by(pref_no) %>%
  add_count() %>%
  filter((nn>40 & n>2)|(nn<=40 & n>1))


##  This function will create Map for selected prefecture.  
## 1 is Hokkaido, 13 is Tokyo, 14 is Kanagawa
submap <- function(pref_num){
  
  if(pref_num==13)  ## If Tokyo remove island 
  prefecture <- japan.map %>% filter(pref_no==pref_num) %>% arrange(-P_NUM) %>% filter(is.na(SICHO))
  else
  prefecture <- japan.map %>% filter(pref_no==pref_num) %>% arrange(-P_NUM)
  
  train.lines.sub <- train.lines.df %>% 
    mutate(pref_no = as.integer(prefs_cd)) %>% filter(pref_no==pref_num)
  selected.pref <- japan.prefecture %>% filter(pref_no==pref_num)
  
  train.summary <- train.lines.sub %>% ungroup() %>% 
    summarise(station.cnt=n(), line.cnt=n_distinct(line.cd))
  
  major.station.selected <- major.station %>% filter(pref_no==pref_num)
  
  pref.map <- prefecture %>% ggplot() + geom_sf(aes(fill=P_NUM), alpha=0.8, size=0.02) +
    scale_fill_viridis_c(end=0.8, option="magma", label=comma, name="Population") +
    theme_map_chi() +
    geom_point(data=train.lines.sub, aes(x=lon, y=lat),color="white",alpha=0.5, shape=4) +
    labs(title=glue('{selected.pref$prefecture_en[1]} : {selected.pref$prefecture_ja[1]}'),
         subtitle = glue("{train.summary$station.cnt[1]} train stations {train.summary$line.cnt[1]} train lines in {selected.pref$prefecture_en[1]}  
                         Most populated city in {selected.pref$prefecture_en[1]} is {prefecture$CITY_ENG[1]} with {round(prefecture$P_NUM[1]/1000)}K in Population")) +
    geom_label_repel(data=major.station.selected, aes(x=lon,y=lat, label=station ),
                     family="Hiragino Sans W2", segment.color="#c0c0c090", fill="#ffffff30")
  print(pref.map)
}

## Testing Area

## I can create map of Kanagawa with 14L
# submap(14L)

base.map <-japan.map %>% ggplot() + geom_sf(aes(fill=P_NUM), alpha=0.8, size=0.01) +
  theme_map_chi() +
  scale_fill_viridis_c(end=0.8, option="magma", label=comma, name="Population") +
  labs(title="Japan (日本)")

base.map


## write it to pdf
cairo_pdf(file="Japan_Prefecture.pdf", width=16, height=9, onefile=T, family="Hiragino Sans W3")

print(base.map)

for (i in c(1L:47L)){
  submap(i)
}
dev.off()






```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

